---
title: "Homework 2"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Problem 1
Read and clean the data:
```{r clean_subway_data}
subway_data = 
  read_csv("./data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv") %>% 
  janitor::clean_names() %>%
  select(line:entry, vending, ada) %>% 
  mutate(entry = recode(entry, "YES" = TRUE, "NO" = FALSE))
subway_data
variable.names(subway_data)
```

The dataset contains the line, station's name, the latitude and longitude of the station, the routes served by the station, whether the entrance is allowed, whether an exit/entrance is with vending, type of the entrance and whether an exit/entrance is ADA compliant.  
My data cleaning steps so far include: load the data by using "read_csv" function, clean up the column names using "janitor::clean_names", select columns that I want to keep, and convert the entry variable from character to a logical variable using "recode" function.  
The dimension (rows x columns) of the resulting dataset is `r dim(subway_data)`.  
These data are not tidy: the route number is spread across 11 columns.
